|

### 2022-05-15 article/article.Rmd
Update article.Rmd

To avoid this problem, in section A.5 of the Supplemental Materials, we show by
simulation that adding controls, especially the variables responsible for the
multiple threshold assignments (in our case, the population in 2003), improves
the consistency and efficiency of the estimates. Relying on this fact, we add
five controls to the estimates: population in 2003; GDP per capita; the number
of seats in 2000; year; and a dummy for Northeast municipalities. The
reason for the first variable is the multiple threshold assignments. We add GDP
per capita because wealthier cities tend to have better public services. The
number of seats in 2000 intends to control that some municipalities could
experience a change provoked by the previous council size, confounding our
estimates. The year and the Northeast dummies were added to improve efficiency.
Adding controls improves efficiency in RDD and also enhances the consistency in
the multiple thresholds RDD \citep{calonico2019regression}.

>>>>

To avoid this problem, in section A.5 of the Supplemental Materials, we show by
simulation that adding controls, especially the variables responsible for the
multiple threshold assignments (in our case, the population in 2003), improves
the consistency and efficiency of the estimates. Relying on this fact, we add
five controls to the estimates: population in 2003; GDP per capita; the number
of seats in 2000; year; and a dummy for Northeast municipalities. The
reason for the first variable is the multiple threshold assignments. We add GDP
per capita because wealthier cities tend to have better public services. The
number of seats in 2000 intends to control that some municipalities could
experience a change provoked by the previous council size, confounding our
estimates. The Northeast dummy was added to control for the fact that the Lula
administration heavily invested in the region from 2003 until 2010, improving 
several development indicators \citep{de2015politica}. The years were added 
to improve efficiency. Moreover, adding controls improves efficiency in RDD
\citep{calonico2019regression} and also enhances the consistency in the 
multiple thresholds RDD.
